# Publications

## Publications track record
```{r}
library(bib2df)
#!> read jorunal articles from bib file
bib_journal <- bib2df::bib2df(here::here("bib", "journal.bib"))
bib_no_journal <- nrow(bib_journal)
#!> read proceedings articles from bib file
bib_proceedings <- bib2df::bib2df(here::here("bib", "proceedings.bib"))
bib_no_proceedings <- nrow(bib_proceedings)

total_pub <- bib_no_journal + bib_no_proceedings

library(scholar)
#!> access my scholar profile
id <- 'upYmy0oAAAAJ&hl'
profile <- get_profile(id)
#!> get my citation history
ct <- get_citation_history(id)
#!> get my publications
pubs <- get_publications(id) %>% as_tibble()
no_pubs_scholar <- nrow(pubs)


#!> access date
access_dttm <- format(Sys.time(), "%d %b %Y")

```

During my career I have published a **total number of `r total_pub` peer-reviewed papers**. Thereof **`r bib_no_journal` publications in peer-reviewed scientific journals** and **`r bib_no_proceedings` in peer-reviewed conference proceedings**. According to Google Scholar (as of `r access_dttm`), these have been **cited a total of `r profile$total_cites` times**, thereof **`r dplyr::last(ct$cites)` times within `r dplyr::last(ct$year)`**.

<br/><br/>

## Articles in Peer-reviewed Journals
*indicates equal author contributions

```{r clean_journal, include=FALSE, warning = FALSE,  message=FALSE}
l <- readLines(here::here("bib", "journal.bib")) %>%
  # !> make author name uniform to allow highlighting with "strong.lua"
  str_replace_all(., "Langbehn, Tom J", "Langbehn, Tom J.") %>%
  str_replace_all(., "Langbehn, Tom J.", "Langbehn, T") %>%
  str_replace_all(., "Langbehn, T.J.", "Langbehn, T") %>%
  str_replace_all(., "T.J. Langbehn", "Langbehn, T")
# !> clean issue numbers that contain the month
pattern <- str_c("\\b", paste0("number = \\{", month.name), "\\b", collapse = "|")
l <- l %>% str_replace_all(., pattern, "number = {")
# !> write to file
cat(l, sep = "\n", file = here::here("bib", "journal.bib"))
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_journals}
:::

\endgroup




## Working Papers under Revision or Review
```{r clean_working_papers, include=FALSE, warning = FALSE,  message=FALSE}
l <- readLines(here::here("bib", "working_paper.bib")) %>%
  # !> make author name uniform to allow highlighting with "strong.lua"
  str_replace_all(., "Langbehn, Tom J", "Langbehn, Tom J.") %>%
  str_replace_all(., "Langbehn, Tom J.", "Langbehn, T") %>%
  str_replace_all(., "Langbehn, T.J.", "Langbehn, T") %>%
  str_replace_all(., "T.J. Langbehn", "Langbehn, T")
# !> clean issue numbers that contain the month
pattern <- str_c("\\b", paste0("number = \\{", month.name), "\\b", collapse = "|")
l <- l %>% str_replace_all(., pattern, "number = {")
# !> write to file
cat(l, sep = "\n", file = here::here("bib", "working_paper.bib"))
```

*in. prep.*  articles are only listed when ready to submit

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_working_paper}
:::

\endgroup


## Articles in Peer-reviewed Conference Proceedings
```{r clean_proceedings, include=FALSE, warning = FALSE,  message=FALSE}
l <- readLines(here::here("bib", "proceedings.bib")) %>%
  # !> make author name uniform to allow highlighting with "strong.lua"
  str_replace_all(., "Langbehn, Tom J", "Langbehn, Tom J.") %>%
  str_replace_all(., "Langbehn, Tom J.", "Langbehn, T") %>%
  str_replace_all(., "Langbehn, T.J.", "Langbehn, T") %>%
  str_replace_all(., "T.J. Langbehn", "Langbehn, T")
# !> clean issue numbers that contain the month
pattern <- str_c("\\b", paste0("number = \\{", month.name), "\\b", collapse = "|")
l <- l %>% str_replace_all(., pattern, "number = {")
# !> write to file
cat(l, sep = "\n", file = here::here("bib", "proceedings.bib"))
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_proceedings}
:::

\endgroup

